Propensity Estimation Matrix Factorization Through Mixed-Quantized Dataset

### 2022-07-21 paper/paper.tex
Add algo.py

\title{Title}

@@

The main contribution of this work is three-fold:
\begin{enumerate}
  \item We design experiments under a simulated environment and shows that a more quantized dataset is more susceptible to selection bias (and thus the MNAR condition.)
  \item We approach the above empirical results from a theoretical lens and explains the complex relationship between quantization, selection bias, and a recommender's performance using tools from information theory.
  \item We propose a cross-dataset learning framework that empowers existing recommender algorithms to make use of the more quantized, implicit data. \textcolor{red}{EXPLAIN MORE HERE}
\end{enumerate}

@@

\section{Theoretical Analysis}

>>>>

\title{Propensity Estimation Matrix Factorization Through Mixed-Quantized Dataset}

@@

The main contribution of this work is two-fold:
\begin{enumerate}
  \item We design experiments under a simulated environment and shows that a more quantized dataset is more susceptible to selection bias (and thus the MNAR condition.)
  \item We propose a cross-dataset learning framework that empowers existing recommender algorithms to make use of the more quantized, implicit data. \textcolor{red}{EXPLAIN MORE HERE}
\end{enumerate}

@@
